Subject-level developmental relationships

### 2024-08-28 2_developmental_analysis.qmd
update filenames

```{r}
library(here)
source(here("helper","common.R"))
d_trial <- readRDS(here("cached_intermediates","1_d_trial"))
d_sub <- readRDS(here("cached_intermediates","1_d_sub"))
```

>>>>

```{r}
library(here)
source(here("helper","common.R"))
d_trial <- readRDS(here("cached_intermediates","1_d_trial.Rds"))
d_sub <- readRDS(here("cached_intermediates","1_d_sub.Rds"))
```

### 2024-08-28 3_developmental_relationships.qmd
update filenames

```{r}
library(here)
source(here("helper","common.R"))
d_sub <- readRDS(here("cached_intermediates","1_d_sub"))
load(here("..", "peekbank-method", "cached_intermediates", "1_cdi_subjects.Rds"))
```

>>>>

```{r}
library(here)
source(here("helper","common.R"))
d_sub <- readRDS(here("cached_intermediates","1_d_sub.Rds"))
load(here("..", "peekbank-method", "cached_intermediates", "1_cdi_subjects.Rds"))
```
